data_collation

### 2024-04-12 scripts/data_collation.Rmd
finished cleanign data

@@

#UPC dataframe does not have month and day so that is why it isn't connecting fully
```

@@

# the one swath data.frame has 115 variables because each species is listed instead of its code, fo you want me to replace with the code and make it wide to long format?

>>>>

# UPC data is cleaned and ready

@@

#UPC data frame does not have month and day so that is why it isn't connecting fully
```

# site information data is cleaned and ready

# remove columns with observer and unneeded data
site.info.dat <- site.info.dat[ -c(12:15) ]

# output updated dataframe
write.csv(site.info.dat, "output/cleaned_data/site.info.data.clean.csv", row.names = FALSE)

@@

# swath dataframe has species names as columns in wide format, need to change names to species codes to combine with other dataframes

# load species names and species code dataframe
species.metadata <- read.csv("data/species_code_metadata.csv")

# Convert species names to codes
for (col in names(swath)) {
  swath[, col] <- species.metadata$code[match(swath[, col], species.metadata$species.substrate)]
}

#some of the species in swath dataframe are common names and species metadata in species names
